---
title             : "Does Double-Hard Debias Keep its Promises? - A Replication Study"
shorttitle        : "Replication: Wang et al. (2020)"

author: 
  - name          : "Kristina Kobrock"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "kkobrock@uni-osnabrueck.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - müssen wir natürlich nicht ausfüllen
     
      
  - name          : "Meike Korsten"
    affiliation   : "1"
    role:
      - ...
      
  - name          : "Sonja Börgerding"
    affiliation   : "1"
    role:
      - ...

affiliation:
  - id            : "1"
    institution   : "University of Osnabrück"

  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Just edit the text! There are several websites that help with (r)markdown, e.g. https://rmarkdown.rstudio.com/.
If you don't want to edit directly, but rather comment use:
<!-- KK: This is a comment. It won't be included in the exported file. -->
Cite using: Wang et al. [-@wang2020doublehard] said that... or simply blablabla [@wang2020doublehard]. References must be added to r-references.bib file. 

## Introduction
- shall we include an abstract?

### Bias in Embeddings
- some text on bias in embeddings and why it's useful to do research in that field
- summary of related approaches (or put it in the discussion ?)

### Motivation
- rough description of the specific study (Wang et al.) & motivation of replication attempt (maybe some general remarks on the need for replication studies)


## Implementation
- task description
- explanation of model and training choices

### Datasets and Preliminaries

### Hard Debias

### Double-Hard Debias


## Evaluation 
- stick to the paper

### Baselines

### Evaluation of Debiasing Performance
### Debiasing in Downstream Applications
#### Coreference Resolution
- no replication possible, no code provided

### Debiasing at Embedding Level
#### The Word Embeddings Association Test (WEAT)
#### Neighborhood Metric
- discuss that this is shady in the discussion part

## Analysis of Retaining Word Semantics
#### Word Analogy
#### Concept Categorization


## Discussion
- analysis of results and evaluation of performance evaluation
- ablation studies (not applicable)
- discuss the results and what could be (partly) replicated and what not


## Conclusion



\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
